---
title: "Assignment 04"
author: "John W. Hoggard"
date: "2020-09-10"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 1

```{r}
library(tidyverse)
iris%>%
  ggplot(aes(x=Sepal.Length,y=Sepal.Width))+
  geom_point()+
  labs(title="Sepal Length vs Sepal Width",
       x="Sepal Length",
       y= "Sepal Width")+
  geom_smooth(method=lm, se=FALSE)
```

Intial analysis indicated there was no real relationship between sepal length and sepal width. Putting a linear regression line shows that there is a slight negative correlation between sepal length and sepal width. More analysis will be necessary to determine if there is any reason for this relationship.

## Problem 2

```{r}
library(tidyverse)
iris%>%
  ggplot(aes(x=Sepal.Length,y=Sepal.Width,
             color=Species))+
  geom_point()+
  labs(title="Sepal Length vs Sepal Width",
       x="Sepal Length",
       y= "Sepal Width")+
  geom_smooth(method=lm, se=FALSE)
```

Intial analysis indicated there was no real relationship between sepal length and sepal width. However, when trying to determine if there were underlying causes for this relationship, it appears as though different species have different relationships with sepal length and width. Seperating out the data by species and adding a regression line helps see the relationship.


## Problem 3

```{r}
library(tidyverse)
iris%>%
  filter(Species=="virginica")%>%
  ggplot()+
  geom_boxplot(aes(x=Sepal.Width, y=Species))+
  labs(title="Sepal Width for virginica",
       x="Sepal Width")
```

The data has a median value of approximatley a 3.0, with a Q1 of approximately 2.8, and a Q3 of approximatley 3.3. 50% of the data falls between the approximate Q1 and Q3 values.

## Problem 4
    
You should also start looking at a basic Exploratory Data Analysis on your data set selected for the first project.  What can you say about the distribution of some of the variables?  What can you say about covariation?
